Resonation Elicits Diffusion: \\Modelling Subjectivity for Retweeting Analysis

### 2014-01-25 retweet_aaai.tex
20140127

Let $G=\left( V,E \right) $ denotes a social network, where $ V $ is a set of users on Twitter, and $ E\subset V\times V $ is a set of directed relationships between users. For each user $ u \in V $, there is a tweets collection $ M_{u} $ denotes his message history. We assume there is a topic space $ T $ containing all topics they talk about, and a sentiment valence space $ O $ for evaluating their opinions towards these topics. 
For the ``subjectivity'' of a user $ u $, we refer to both topics of interest and opinions articulated in his tweets collection $ M_{u} $.  
\begin{definition}[Subjective Model]
The subjective model $ P \left( u \right) $ of a user $u \in V $, is the combination of a set of topics $\left\lbrace  t_{i} \left( i \in \lbrace1 \cdots n \rbrace \right)  \right\rbrace $ the user talks about in a topic space $T$ and the user's opinion $o_{i}$ towards each topic $ t_{i} $. 
\begin{equation}
\label{usermodel}
P \left( u \right) = \lbrace \left( t_{i}, w_{u} \left( t_{i} \right), d_{u,t_{i}} \left( o_{i} \right) \right) \,\vert  t_{i} \in T, \, o_{i} \in O \rbrace
\end{equation}
where:
\begin{itemize}
\item with respect to the given user $ u $,  for each topic $t_{i} \in T$, its  weight $ w_{u} \left( t_{i} \right)$ represents the distribution of the user's interests on it, with $ \sum_{i=1}^{|T|}w_{u} \left( t_{i} \right)=1 $.
\item opinion of the user towards topic $t_{i}$ is modeled as a topic-dependent sentiment distribution  $d_{u,t_{i}} \left( o_{i} \right)$ over sentiment valence space $ O $.
\end{itemize}
\end{definition}
Figure~\ref{fig0} is a visualized subjective model of a user. 
\begin{figure}[htb]
%\centering
\includegraphics[width=3.8in,height=2.5in]{fig1.pdf}
\caption{The left subgraph denotes two topics a user tweets about with weights $ \left( w_{u}\left( t_{23} \right)=0.43, w_{u}\left( t_{86} \right)=0.57\right)  $. the right subgraph denotes opinions towards two topics: for topic 23, $ ( d_{u,t_{23}} \left( o_{2} \right)=0.1, d_{u,t_{23}} \left( o_{4} \right)=0.5,d_{u,t_{23}} \left( o_{5} \right)=0.3,d_{u,t_{23}} \left( o_{6} \right)=0.1) $; for topic 86, $ \left( d_{u,t_{86}} \left( o_{4} \right)=0.66, d_{u,t_{86}} \left( o_{5} \right)=0.34 \right) $.}
\label{fig0}
\end{figure}

@@

We take 5,214 retweeters in our dataset who retweet at least one target tweet as positive instances, and randomly sample 5,214 negative instances from the 40,317 followers who do not retweet any target tweet.
The balance dataset of all positive and negative instances is randomly divided into five parts for 5-fold cross-validation. 
We use the logistic regression classifier of Scikit-learn machine learning package \cite{scikit-learn} for training and testing.
Accuracy is our evaluation metric, and the result is listed in Table~\ref{tab3}.
\begin{table}[h]
\centering
\caption{Comparison of prediction accuracy for different models. }
\label{tab3}
\begin{tabular}{|c|c|}
\hline
Feature & Accuracy(\%) \\
\hline
TF-IDF & 60.85  \\
entity & 68.76 \\
hashtag & 59.12  \\
$ sim_{sub} \left( m,u \right) $ & 73.88\\
$ sim_{sub}\left( u_{a},u \right)  $ & 70.04\\
$ sim_{sub}\left( m,u_{a} \right)  $ &69.64\\
$ sim_{all}  $ &\textbf{75.64}\\
\hline
\end{tabular}
\end{table}

>>>>

Let $G=\left( V,E \right) $ denotes a social network, where $ V $ is a set of users on Twitter, and $ E\subset V\times V $ is a set of directed relationships between users. For each user $ u \in V $, there is a tweets collection $ M_{u} $ denotes his message history. We assume there is a topic space $ T $ containing all topics they talk about, and a sentiment valence space $ O $ for evaluating their opinions towards these topics. 
For the ``subjectivity'' of a user $ u $, we refer to both topics of interest and opinions articulated in his tweets collection $ M_{u} $.  
\begin{definition}[Subjective Model]
The subjective model $ P \left( u \right) $ of a user $u \in V $, is the combination of a set of topics $\left\lbrace  t_{i} \left( i \in \lbrace1 \cdots n \rbrace \right)  \right\rbrace $ the user talks about in a topic space $T$ and the user's opinion $o_{i}$ towards each topic $ t_{i} $. 
\begin{equation}
\label{usermodel}
P \left( u \right) = \lbrace \left( t_{i}, w_{u} \left( t_{i} \right), d_{u,t_{i}} \left( o_{i} \right) \right) \,\vert  t_{i} \in T, \, o_{i} \in O \rbrace
\end{equation}
where:
\begin{itemize}
\item with respect to the given user $ u $,  for each topic $t_{i} \in T$, its  weight $ w_{u} \left( t_{i} \right)$ represents the distribution of the user's interests on it, with $ \sum_{i=1}^{|T|}w_{u} \left( t_{i} \right)=1 $.
\item opinion of the user towards topic $t_{i}$ is modelled as a topic-dependent sentiment distribution  $d_{u,t_{i}} \left( o_{i} \right)$ over sentiment valence space $ O $.
\end{itemize}
\end{definition}
Figure~\ref{fig0} is a visualized subjective model of a user in a 100 topics space and a $ [0,8] $ sentiment valence space. 
\begin{figure}[htb]
%\centering
\includegraphics[width=3.8in,height=2.5in]{fig1.pdf}
\caption{The left subgraph denotes two topics a user tweets about with weights $ \left( w_{u}\left( t_{23} \right)=0.43, w_{u}\left( t_{86} \right)=0.57\right)  $. the right subgraph denotes opinions towards two topics: for topic 23, $ ( d_{u,t_{23}} \left( o_{2} \right)=0.1, d_{u,t_{23}} \left( o_{4} \right)=0.5,d_{u,t_{23}} \left( o_{5} \right)=0.3,d_{u,t_{23}} \left( o_{6} \right)=0.1) $; for topic 86, $ \left( d_{u,t_{86}} \left( o_{4} \right)=0.66, d_{u,t_{86}} \left( o_{5} \right)=0.34 \right) $.}
\label{fig0}
\end{figure}

@@

We take 5,214 retweeters in our dataset who retweet at least one target tweet as positive instances, and randomly sample 5,214 negative instances from the 40,317 followers who do not retweet any target tweet.
The balance dataset of all positive and negative instances is randomly divided into five parts for 5-fold cross-validation. 
We use the logistic regression classifier of Scikit-learn machine learning package \cite{scikit-learn} for training and testing.
Accuracy is our evaluation metric, and the result is listed in Table~\ref{tab3}.
\begin{table}[h]
\centering
\caption{Comparison of prediction accuracy for different models. }
\label{tab3}
\begin{tabular}{|c|c|}
\hline
Feature & Accuracy(\%) \\
\hline
TF-IDF & 62.85  \\
entity & 68.76 \\
hashtag & 59.12  \\
$ sim_{sub} \left( m,u \right) $ & 73.88\\
$ sim_{sub}\left( u_{a},u \right)  $ & 70.04\\
$ sim_{sub}\left( m,u_{a} \right)  $ &69.64\\
$ sim_{all}  $ &\textbf{75.64}\\
\hline
\end{tabular}
\end{table}
